Twitter Trader - Correlating \\ Stocks with Twitter Activity

### 2012-11-16 paper/paper.tex
updated paper and constants

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\section{System Breakdown}

@@

@@

\section{ Acknowledgments}
Blah blah.

>>>>

%File: formatting-instruction.tex
\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\nocopyright
\frenchspacing
\pdfinfo{
/Title (Twitter Trader)
/Subject (AAAI Publications)
/Author (Curtis Ullerich, Daniel Stiner, Brandon Maxwell)}
\setcounter{secnumdepth}{0}  
\begin{document}

@@

\section{System Breakdown}
\textbf{Corpus creation}\\
\textbf{Data aggregation and classification}\\
\textbf{Decision-making}\\

@@

A major component of this is corpus creation. Using Twitter's streaming API, we pull for tweets based on keyword. Using our trained models, we classify each tweets with the highest-confidence company and sentiment labels, including the confidences. We created a simple web interface for accessing the database in order to human-verify classifications for insertion into the database. \href{http://danielstiner.com:9001/company-yes-no.html#/classified/random/company/confidence/.2:1/count/1}{This page} displays a random classified tweet and asks the user if the tweet is correctly classified.

@@

\section{ Acknowledgments}
